\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[finale]{changes}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{linkcolor=blue}

\usepackage{xeCJK}
\usepackage{fontspec}
%\setmainfont{Times New Roman} 
\setCJKmainfont{LiSu}
\usepackage{tikz}

\usepackage[numbers, super, sort&compress]{natbib}
\bibliographystyle{plain}


%opening
\title{Instantaneous rock transformations in the deep crust driven by reactive fluid flow 冬练三九}
\author{A. Beinlich2, T. John, J. C. Vrijmoed, M. Tominaga, T. Magna, Y. Y. Podladchikov}

\begin{document}

\maketitle

% d
\begin{abstract}
Fluid–rock interactions are a  fundamental component of geodynamic processes. They link mass and energy transfer with large- scale tectonic deformation and drive mineral deposit formation, carbon sequestration and rheological changes of the litho- sphere. Spatial evidence indicates that fluid–rock interactions operate on length scales that range from the grain boundary to tectonic plates, but the timescales of regional fluid–rock interactions remain essentially unconstrained. Here we present obser- vations from an exceptionally well-exposed fossil hydrothermal \replaced{system from an ophiolite sequence}{replaced text} in northern Norway that we use to inform a multielement advection–diffusion–reaction transport model. We calculated the velocity of the fluid-driven reaction fronts and found that they \deleted{can propagate at} up to 10 cm per year, equivalent to the fastest tectonic plate motion and mid-ocean-ridge spreading rates. Propagation through the low-permeability rocks of the mid-crust is facilitated by a transient, reaction-induced permeability increase. \added{new added text} We conclude that large-scale fluid-mediated rock transformations in continental col- lision and subduction zones occur on timescales of tens of years when reactive fluids are present. We infer that natural carbon sequestration, ore deposit formation and transient and long-term petrophysical changes of the crust proceed instantaneously, from a geological perspective.
\end{abstract}

\input{main_text}

%\autoref{fig:fig1}


\bibliography{refs.bib}

\end{document}
